SDR enhancement by clouds

### 2024-03-07 article/article.Rmd
Commit 2024-03-07 19:17

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
For this reason, we decided to use the Libradtran....cite..... model with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA ....cite..... and Earth - Sun distance calculated by Astropy....cite......
We simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer (afglms)" and "AFGL atmospheric constituent profile, midlatitude winter (afglmw)"....cite...... .

>>>>

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
For this reason, we decided to use the Libradtran model [@Emde2016], with monthly climatological data for AOD and water column from AERONET [@Giles2019; @Buis1998]. Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA [@Coddington2005] and Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].
We have simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and "AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986]. 
We used the solar spectra of
